---
title: "Assignment 2"
author: "Vishnu Prasanth Reddy Patur"
date: "9/11/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r echo=FALSE , message=FALSE, warning=FALSE, packages}
#***********Question_1A***************

#install.packages('ggplot2')
# install.packages("ggpubr")
# install.packages('magrittr')
library(ggpubr)
library(ggplot2)
library(knitr)

setwd('C:/Users/vipra/Desktop/SElf Learning/R_Self/datasets')
Assig<-read.csv ('HMEQ.csv')
```

## Question : 1A

```{r }

summary_stat_func <-function(x){
  mean_1 <- mean(x,na.rm = TRUE)
  median_1<-median(x,na.rm = TRUE)
  std_1 <- sd(x,na.rm= TRUE)
  if (mean_1>median_1){
    skewness='Right Skewed'
  }
  if (mean_1<median_1){
    skewness ='Left Skewed'
  }
  a<-sum(as.numeric(is.na(x)))
  percentage_1<-(a/nrow(Assig))*100
  stats<- c(mean_1,median_1,std_1,skewness,percentage_1)
  return(stats)
}



req_attrib<-c("LOAN","MORTDUE","VALUE","YOJ","CLAGE","DEBTINC")
data_sub<- subset(Assig,select=req_attrib)
result<-apply(data_sub, 2, summary_stat_func)
rownames(result)<-c('Mean','Median','Standard Deviation','Skewness','Missing Value Percentage')
result_1a<-as.data.frame(result)

kable(result_1a)


```




## Question : 1B
```{r }
#***********Question_1B***************
data_assin_1b<-subset(Assig,Assig$BAD==1,select = req_attrib)
result<-apply(data_assin_1b, 2, summary_stat_func)
rownames(result)<-c('Mean','Median','Standard Deviation','Skewness','Missing Value Percentage')
result_1b<-as.data.frame(result)
kable(result_1b)

```



## Question : 1C
```{r }
#***********Question_1C***************
data_assin_1b<-subset(Assig,Assig$BAD==0,select = req_attrib)
result<-apply(data_assin_1b, 2, summary_stat_func)
rownames(result)<-c('Mean','Median','Standard Deviation','Skewness','Missing Value Percentage')
result_1c<-as.data.frame(result)
kable(result_1c)

```


## Question : 2A

```{r}

#***********Question_2A***************
req_2<-c('BAD', 'JOB', 'DELINQ', 'NINQ','CLNO')
Ass_2 <-subset(Assig,select = req_2)
Ass_2[is.na(Ass_2)]<-'NA'
Ass_2$JOB<-as.character(Ass_2$JOB)
Ass_2$JOB[Ass_2$JOB==""]<-'NA'


#Frequency table of Variables
kable(xtabs(~BAD,data = Ass_2),caption = 'BAD Frequency Table')
kable(xtabs(~JOB,data = Ass_2),caption = 'JOB Frequency Table')
kable(xtabs(~DELINQ,data = Ass_2),caption = 'DELINQ Frequency Table')
kable(xtabs(~NINQ,data = Ass_2),caption='NINQ Frequency Table')
kable(xtabs(~CLNO,data = Ass_2),caption='CLNO Frequency Table')


```

## Question : 2B

```{r}
#***********Question_2B***************

kable(xtabs(~JOB + BAD, data = Ass_2),caption=' two-way contingency table of the variable BAD and JOB')
kable(xtabs(~DELINQ + BAD, data = Ass_2),caption='two-way contingency table of the variable BAD and DELINQ')
kable(xtabs(~NINQ + BAD, data = Ass_2),caption='two-way contingency table of the variable BAD and NINQ')
kable(xtabs(~CLNO + BAD, data = Ass_2),caption='two-way contingency table of the variable BAD and CLNO')
```


## Question : 3A

```{r }

#***********Question_3A***************

hist(Assig$LOAN, # histogram
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = "LOAN",
 ylab = "Probability",
 main = "Histogram of LOAN with imposed density lines")
lines(density(Assig$LOAN), # density plot
 lwd = 3, # thickness of line
 col = "red")
#curve(dnorm(, mean=mean(data$Ozone), sd=sd(data$Ozone)), add=T)
lines(Assig$LOAN,dnorm(Assig$LOAN, mean=mean(Assig$LOAN), sd=sd(Assig$LOAN)),col='blue',lwd=3)
legend("topright", c("Normal Density", "Kernal Density"), fill=c("blue", "red"))
```



## Question : 3B

```{r }

mort<-na.omit(Assig$MORTDUE)


hist(mort, # histogram
  breaks = 125,
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = "Mortdue",
 ylab = "Probability",
 xlim = c(2000,250000),
 main = "Histogram of MORTDUE with imposed density lines")
lines(density(mort), # density plot
 lwd = 3, # thickness of line
 col = "red")
points(seq(min(mort),max(mort),length.out = 10000),
       dnorm(seq(min(mort),max(mort),length.out = 10000),
             mean(mort),sd(mort)),type="l",col="blue",lwd=2)
legend("topright", c("Normal Density", "Kernal Density"), fill=c("blue", "red"))


```




## Question : 3C
```{r  }

value<-na.omit(Assig$VALUE)


hist(value, # histogram
  breaks = 125,
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = "value",
 ylab = "Probability",
 xlim = c(0,400000),
 main = "Histogram of value with imposed density lines")
lines(density(value), # density plot
 lwd = 3, # thickness of line
 col = "red")
points(seq(min(value),max(value),length.out = 1000),
       dnorm(seq(min(value),max(value),length.out = 1000),
             mean(value),sd(value)),type="l",col="blue",lwd=2)
legend("topright", c("Normal Density", "Kernal Density"), fill=c("blue", "red"))

```




## Question : 3D
```{r }

clage<-na.omit(Assig$CLAGE)


hist(clage, # histogram
  breaks = 125,
 col="peachpuff", # column color
 border="black",
 prob = TRUE, # show densities instead of frequencies
 xlab = "CLAGE",
 ylab = "Probability",
 xlim = c(0,750),
 main = "Histogram of CLAGE with imposed density lines")
lines(density(clage), # density plot
 lwd = 3, # thickness of line
 col = "red")
points(seq(min(clage),max(clage),length.out = 500),
       dnorm(seq(min(clage),max(clage),length.out = 500),
             mean(clage),sd(clage)),type="l",col="blue",lwd=2)
legend("topright", c("Normal Density", "Kernal Density"), fill=c("blue", "red"))

```



## Question : 4A

```{r }

Assig_1<-na.omit(Assig)
model<-lm(Assig_1$LOAN ~ Assig_1$MORTDUE)


ggplot(Assig_1,aes(Assig_1$MORTDUE,Assig_1$LOAN))+
  geom_point(size = 0.8, pch = 4,color='blue')+
  geom_smooth(method = lm,color='red')+
  xlim(min(Assig_1$MORTDUE),max(Assig_1$MORTDUE))+
  ggtitle("LOAN VS MORTDUE")+
  xlab('MORTDUE')+
  ylab('LOAN')





```




## Question : 4B
```{r }

Assig_1<-na.omit(Assig)
model<-lm(Assig_1$LOAN ~ Assig_1$VALUE)


ggplot(Assig_1,aes(Assig_1$VALUE,Assig_1$LOAN))+
  geom_point(size = 0.75, pch = 3,color='blue')+
  geom_smooth(method = lm,color='red')+
  ggtitle("LOAN VS VALUE")+
  xlim(70000,512650)+
  xlab('VALUE')+
  ylab('LOAN')




```




## Question : 4C
```{r }

Assig_1<-na.omit(Assig)
model<-lm(Assig_1$LOAN ~ Assig_1$YOJ)


ggplot(Assig_1,aes(Assig_1$YOJ,Assig_1$LOAN))+
  geom_point(size = 0.75, pch = 4,color='blue')+
  geom_smooth(method = lm,color='red')+
  ggtitle("LOAN VS YOJ")+
  xlim(0,41)+
  xlab('YOJ')+
  ylab('LOAN')



```



## Question : 4D

```{r }
Assig_1<-na.omit(Assig)
model<-lm(Assig_1$LOAN ~ Assig_1$CLAGE)


ggplot(Assig_1,aes(Assig_1$CLAGE,Assig_1$LOAN))+
  geom_point(size = 0.75, pch = 4,color='blue')+
  geom_smooth(method = lm,color='red')+
  ggtitle("LOAN VS CLAGE")+
  xlim(0,max(Assig_1$CLAGE))+xlab('CLAGE')+
  ylab('LOAN')
  
    


```



## Question : 4E

```{r  }

Assig_1<-na.omit(Assig)
model<-lm(Assig_1$LOAN ~ Assig_1$DEBTINC)


ggplot(Assig_1,aes(Assig_1$DEBTINC,Assig_1$LOAN))+
  geom_point(size = 0.75, pch = 4)+
  geom_smooth(method = lm,color='red')+
  ggtitle("LOAN VS DEBTINC")+
  xlim(0,max(Assig_1$DEBTINC))+
  xlab('DEBTINC')+
  ylab('LOAN')



```




## Question : 5

```{r}

data_assin<-na.omit(Assig)
# set.seed(1234)
# sample_index<-sample(1:nrow(data_assin),1500)
# sample_data<-data_assin[sample_index,]
# data_assin<-sample_data
fit = glm(BAD ~ LOAN, data=data_assin, family=binomial)
predicted<-predict(fit,type='response')
plot(BAD~LOAN, data=data_assin, col="black")
lines(data_assin$LOAN, predicted, col="red2", lwd=2)
  
boxplot(data_assin$LOAN~data_assin$BAD, xlab = 'BAD       0 = Fraudulant, 1 = Not Fraudulant', ylab = 'Loan')
```

### inference : 
it's hypothetical to come to a conclusion by considering `LOAN` as a predictor and `BAD` as response, but from the plot it's noticable that the logistic regression curve is tending towards `0` and more data points above maximum value for `BAD=0` compared to `BAD=1` which can be infered that more `LOAN` the customer take, more fraudulent they tend to be.



```{r}

```







